Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-11-05 revision-1/automation.tex
Add files via upload

Since $|\runs(\prog)|$ grows exponentially in the size of
$\flips(\prog)$, scalability to larger programs is a concern.  However
computation of $\runs$ is amenable to optimizations, especially
parallelization- rather than computing the truth table
``horizontally'', it can be computed ``vertically''. We can rewrite
$\minifed$ programs $\prog$ to stratified Datalog programs, where
$\runs(\prog)$ is equivalent to set of least Herbrand models obtained
by representing different random tapes and input secrets as different
fact bases. Details of this rewrite are provided in Appendix
\ref{section-bruteforce}. The model for each fact base can be computed
independently and in parallel, with the potential to apply other
matrix optimizations developed in recent work on HPC for Datalog
\cite{sakama2017linear,aspis2018linear,nguyen2022enhancing,nguyen2021efficient}.

@@

We will use \emph{certification} to refer to algorithmic methods of
verifying properties of $\minifed$ protocols, vs.~manual methods. For
the sake of clarity we make the following definition:
\begin{definition}
  A predicate $\phi$ on $\minifed$ protocols is \emph{certifiable} iff
  there exists an algorithm $A$ such that $A(\prog)$ iff $\phi(\prog)$,
  and a safe protocol $\prog$ is \emph{certified for $\phi$} iff
  $A(\prog)$ holds.
\end{definition}

>>>>

Since $|\runs(\prog)|$ grows exponentially in the size of
$\flips(\prog)$, scalability to larger programs is a concern.  However
computation of $\runs$ is amenable to optimizations, especially
parallelization- rather than computing the truth table
``horizontally'', it can be computed ``vertically''. We can rewrite
$\minifed$ programs $\prog$ to stratified Datalog programs, where
$\runs(\prog)$ is equivalent to the set of least Herbrand models obtained
by representing different random tapes and input secrets as different
fact bases. Details of this rewrite are provided in Appendix
\ref{section-bruteforce}. The model for each fact base can be computed
independently and in parallel, with the potential to apply other
matrix optimizations developed in recent work on HPC for Datalog
\cite{sakama2017linear,aspis2018linear,nguyen2022enhancing,nguyen2021efficient}.

@@

We will use \emph{certification} to refer to algorithmic methods of
verifying properties of $\minifed$ protocols, vs.~manual methods. For
the sake of clarity, we make the following definition:
\begin{definition}
  A predicate $\phi$ on $\minifed$ protocols is \emph{certifiable} iff
  there exists an algorithm $A$ such that $A(\prog)$ iff $\phi(\prog)$,
  and a safe protocol $\prog$ is \emph{certified for $\phi$} iff
  $A(\prog)$ holds.
\end{definition}

### 2023-11-05 revision-1/bruteforce.tex
Add files via upload

\section{Brute Force Computation of Program Distributions}
\label{section-bruteforce}

We first explore a brute force approach to automatically verifying
program behaviour, the first step of which is to compute the basic
distribution of a program $\prog$. The program distribution
$\progd(\prog)$ can obviously be automatically derived from that, as
can be any of its marginal or conditional distributions. In this
Section, we consider two automated mechanisms for deriving
$\progd(\prog)$ in this way. The first is through a straightforward
computation of all final program memories.  The second approach
rewrites $\minifed$ programs to stratified Datalog programs, that are
amenable HPC optimizations such as parallelization and GPU matrix
computations as shown in recent work
\cite{sakama2017linear,aspis2018linear,nguyen2022enhancing,nguyen2021efficient}.

\begin{fpfig}[t]{Truth table visualizations of $\runs(\prog_{\ref{example-otp}})$ (L) and
    $\runs(\prog_{\ref{example-lambda-obliv}(a)})$ (R).}{fig-basic-distributions}
{\footnotesize
  $$
  \begin{array}{cc}
    \begin{array}{cccccc}
      \verb+s[1,0]+ & \verb+f[1,0]+ & \verb+v[2,0]+  & \verb+v[2,1]+ & \verb+v[2,2]+ & \verb+v[0,0]+\\
      \hline
      0 & 0 & 0 & 0 & 0 & 0 \\ 
      0 & 1 & 1 & 1 & 0 & 1 \\ 
      1 & 0 & 0 & 1 & 1 & 1 \\ 
      1 & 1 & 1 & 0 & 1 & 0
    \end{array}
    & 
    \begin{array}{ccccc}
      \verb+s[1,s]+ & \verb+f[1,sx]+ & \verb+f[1,sy]+ & \verb+v[0,0]+ & \verb+v[0,1]+ \\
      \hline
      0 & 0 & 0 & 0 & 0 \\ 
      0 & 0 & 1 & 1 & 0 \\ 
      0 & 1 & 0 & 0 & 1 \\ 
      0 & 1 & 1 & 1 & 1 \\
      1 & 0 & 0 & 0 & 0 \\ 
      1 & 0 & 1 & 0 & 0 \\ 
      1 & 1 & 0 & 1 & 1 \\ 
      1 & 1 & 1 & 1 & 1  
    \end{array}
  \end{array}
  $$
}
\end{fpfig}

%The basic distribution of a program $\prog$ is based on the
%final memories resulting from any run of $\prog$, denoted
%$\runs(\prog)$.
%\begin{definition}
%  Given $\prog$ with $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$:
%  $$
%  \runs(\prog) \defeq \{ \store \in \mems(S\cup F \cup V) \mid \config{\store_{S \cup F}}{\prog} \redxs \config{\store}{\varnothing} \}
%  $$
%\end{definition}

As we've observed, $\runs(\prog)$ can be represented in a truth table
form, as illustrated in Figure \ref{fig-basic-distributions}.

\begin{fpfig}[t]{Filtering memories that satisfy a boolean expression.}{fig-solve}
\begin{eqnarray*}
\solve{\stores}{\etrue} &=& \stores\\
\solve{\stores}{\efalse} &=& \varnothing\\
\solve{\stores}{\flip{\cid}{w}} &=& \{ \store \in \stores \mid \store(\flip{\cid}{w}) \} \\
\solve{\stores}{\secret{\cid}{w}} &=& \{ \store \in \stores \mid \store(\secret{\cid}{w}) \} \\
\solve{\stores}{\view{\cid}{w}} &=& \{ \store \in \stores \mid \store(\view{\cid}{w}) \} \\
\solve{\stores}{\oracle{w}} &=& \{ \store \in \stores \mid \store(\oracle{w}) \} \\
\solve{\stores}{(\enot\ \be)} &=& \stores - (\solve{\stores}{\be})\\
\solve{\stores}{(\be_1\ \eand\ \be_2)} &=& (\solve{\stores}{\be_1}) \cap (\solve{\stores}{\be_2}) \\
\solve{\stores}{(\be_1\ \eor\ \be_2)} &=& (\solve{\stores}{\be_1}) \cup (\solve{\stores}{\be_2}) \\
\solve{\stores}{(\be_1\ \exor\ \be_2)} &=&
 ((\solve{\stores}{\be_1}) \cap (\stores - \solve{\stores}{\be_2})) \cup\\
 && ((\stores - \solve{\stores}{\be_1}) \cap (\solve{\stores}{\be_2})) \\
\solve{\stores}{\select{\be_1}{\be_2}{\be_3}} &=&
 ((\solve{\stores}{\be_1}) \cap (\solve{\stores}{\be_2})) \cup \\
 && ((\stores - \solve{\stores}{\be_1}) \cap (\solve{\stores}{\be_3})) \\
\solve{\stores}{\OT{\be_1}{\be_2}{\be_3}} &=&
 ((\solve{\stores}{\be_1}) \cap (\solve{\stores}{\be_2})) \cup\\
 && ((\stores - \solve{\stores}{\be_1}) \cap (\solve{\stores}{\be_3}))
\end{eqnarray*}
\end{fpfig}

\subsection{Method 1: Inductive Computation of $\runs(\prog)$}
\label{section-bruteforce-tables}

Here we describe a straightforward technique for obtaining program
distributions $\progd(\prog)$ through direct computation of
$\runs(\prog)$. Although we could obtain $\runs(\prog)$ simply by
executing $\prog$ given all random tapes and input secrets, the method
we describe here is empirically more efficient (though still
exponential in the length of the random tape), and also supports the
translation to Datalog described in Section
\ref{section-bruteforce-datalog}. An implementation of these
techniques along with Examples from Sections
\ref{section-minicat-examples} and \ref{section-metalang-ygc} is
available online\footnote{URL redacted for double-blind review.}.

In Figure \ref{fig-solve} we define the algorithm $\solve{\stores}{\be}$
which filters $\stores$ based on satisfaction of $\be$. This algorithm
is fundamental to our brute force methods. It's correctness is characterized
as follows. 
\begin{lemma}
  \label{lemma-solves}
  For all $\stores$ and $\be$ with $\vars(\be) \subseteq \dom(\stores)$,
  $(\solve{\stores}{\be}) = \{ \store \in \stores \ \mid\ \lcod{\store,\be}{\cid} = 1 \}$
  for some $\cid$.
\end{lemma}
\begin{proof}
  Since we assume safety of programs we can assume that all variables in $\be$ have the
  same owner $\cid$. The result otherwise follows in a straightforward manner by induction
  on $\be$. 
\end{proof}

In order to automatically obtain $\runs(\prog)$, we can do a left
folding of $\solve$ across $\prog$, inductively extending memories
with valid view assignments in the order of their definition.
We can then use this to compute $\progd(\prog)$. We denote
these computations as $\cruns$ and $\cprogd$ respectively.
\begin{lemma}
  \label{lemma-cruns}
  Given $\prog$ where $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$. Define:
  \begin{eqnarray*}
    {tt}\ \ \stores\ (\eassign{\view{\cid}{w}}{\be}) &\defeq& \begin{array}{l}
      \mathrm{let}\ \stores' = \solve{\stores}{\be} \ \mathrm{in}\\
      \ \ \{\extend{\store}{\view{\cid}{w}}{1} \mid \store \in \stores' \}\ \cup\\
      \ \ \{\extend{\store}{\view{\cid}{w}}{0} \mid \store \in \stores - \stores' \}\end{array}\\[2mm]
    \cruns(\prog) &\defeq& \mathit{foldl}\ {tt}\ \mems(S \cup F)\ \prog
  \end{eqnarray*}
  Then $\cruns(\prog) = \runs(\prog)$.
\end{lemma}
\begin{proof}
  By Lemma \ref{lemma-solves} and induction on the length of $\prog$. 
\end{proof}
\begin{lemma}
  \label{lemma-cprogd}
  Given $\prog$ where $\iov(\prog) = S \cup V$ and $\flips(\prog) = F$. Define
  $\cprogd(\prog)$ as the distribution $\pmf$
  where for all $\store \in \mems(S\cup F \cup V)$:
  $$
  \pmf(\store) = \begin{cases}1/2^{|S \cup F|} & \text{if\ } \store \in
    \cruns(\prog) \\ 0 & \text{otherwise} \end{cases} 
  $$
  Then:
  $$
  \cprogd(\prog) = \progd(\prog)
  $$
\end{lemma}
\begin{proof}
  Immediately by Lemma \ref{lemma-cruns} and Definition \ref{def-progd}.
\end{proof}

%%% I moved the following to automation.tex - chris
\begin{comment}
We have used the code for $\cruns$ and $\cprogd$ extensively to design and
verify the examples in this paper. We will discuss other examples in
Section \ref{section-composition}, but here we note that we've verified
passive security of Examples \ref{example-he} and \ref{example-OT}-
for the former, this is well-known so the result is a simple proof-of-concept,
but the latter is a new (though unsurprising) result, having not been
directly proven in \cite{barthe2019probabilistic}. The method for
verifying $\NIMO$ described here generalizes to any $\prog$. 
\begin{lemma}[Automated Verification of Passive Security]
  \label{lemma-bruteforce-nimo}
  $\prog_{\ref{example-he}}$ and $\prog_{\ref{example-OT}};\eassign{\outv}{\vx{2}{mc}}$ are
  passive secure.
\end{lemma}
\begin{proof}
  For both $\prog \in \{
  \prog_{\ref{example-he}},\prog_{\ref{example-OT}};\eassign{\outv}{\vx{2}{mc}}\}$
  we compute $\cruns(\prog)$ and $\cprogd(\prog)$ and then verify
  $\NIMO(\prog)$ using the following algorithm. Given $\iov(\prog) = S
  \cup V$ and $\flips(\prog) = F$, we enumerate all memories $\store
  \in \cruns(\prog)$, then enumerate all partitions of clients into
  sets $H$,$C$ such that $|C| \le |H|$ and $0 \in C$, and then check:
  $$
  \cprogd(\prog)(\store_{S_H}|\store_{S_C \cup \{\outv\}}) =
  \cprogd(\prog)(\store_{S_H}|\store_{S_C \cup V_C})
  $$
  for each $H,C,\store$. The result follows by Lemma \ref{lemma-cprogd}, Lemma \ref{lemma-nimo}, and
  Theorem \ref{theorem-nimo}.
\end{proof}

\end{comment}

\subsection{Method 2: Conversion to Datalog}
\label{section-bruteforce-datalog}

>>>>

\section{Rewriting $\minicat$ to Stratified Datalog}
\label{section-bruteforce}

### 2023-11-05 revision-1/conclusion.tex
Add files via upload

We believe this line of research is promising for future work,
including extensions to malicious security, and to larger fields and
arithmetic circuits. HPC optimizations of program distribution
calculations, to support analysis of larger circuit components, is
another interesting direction for future work.

>>>>

We believe this line of research is promising for future work,
including extensions to malicious security, and to larger fields and
arithmetic circuits. HPC optimization of program distribution
calculations, to support analysis of larger circuit components, is
another interesting direction for future work.

### 2023-11-05 revision-1/gmw.tex
Add files via upload

\begin{fpfig}[t]{2-Party GMW Circuit Library with And gate.}{fig-gmw}
{\footnotesize
  \begin{verbatimtab}
    encodegmw(in1,in2) {
      v[1, in1 || "out"] := s[1,in1] xor flip[1,in1];
      v[2, in1 || "out"] := flip[1,in1];
      v[1, in2 || "out"] := s[2,in2] xor flip[2,in2];
      v[2, in2 || "out"] := flip[2,in2]
      { shares1 = { c1 = v[1, in1 || "out"]; c2 = v[2, in1 || "out"] };
        shares2 = { c1 = v[1, in2 || "out"]; c2 = v[2, in2 || "out"]} } 
    }

@@

    decodegmw(shares) { v[0,"output"] := shares.c1 xor shares.c2 }
  \end{verbatimtab}
}
\end{fpfig}

>>>>

\begin{fpfig}[t]{2-Party GMW circuit library with And gate (T), and type annotations (B).}{fig-gmw}
{\footnotesize
  \begin{verbatimtab}
    encodegmw(in1,in2) {
      v[1, in1 || "out"] := s[1,in1] xor flip[1,in1];
      v[2, in1 || "out"] := flip[1,in1];
      v[1, in2 || "out"] := s[2,in2] xor flip[2,in2];
      v[2, in2 || "out"] := flip[2,in2]
      { shares1 = { c1 = v[1, in1 || "out"]; c2 = v[2, in1 || "out"] };
        shares2 = { c1 = v[1, in2 || "out"]; c2 = v[2, in2 || "out"]} } 
    }

@@

    decodegmw(shares) { v[0,"output"] := shares.c1 xor shares.c2 }   \end{verbatimtab}
}

\rule{130mm}{0.5pt}

{\footnotesize
  \begin{verbatimtab}
   encodegmw   : string(gid) * string(gid)

   andtablegmw : { k = bool[i]; p = bool[i] }

   andgmw      : string(gid) *  { c1 = bool[1]; c2 = bool[2] } * { c1 = bool[1]; c2 = bool[2] }

   decodegmw   : { c1 = bool[1]; c2 = bool[2] }  \end{verbatimtab}
}
\end{fpfig}

### 2023-11-05 revision-1/intro.tex
Add files via upload

We distinguish between \emph{extensional} vs.~\emph{intensional}
properties and analysis of MPC protocols. By extensional, we mean
simulator security itself as well as analysis concerned with the use
and interaction of complete secure protocols. By intensional, we mean
analysis and inner workings of protocols themselves

@@

\paragraph{Hyperproperty formulation.} In Section \ref{section-pmf} we
formulate \emph{program distributions}, a formalism for expressing
dependencies between secrets and views, useful for expressing
intensional characteristics of protocols and precisely quantifying
allowable information leakage in terms of protocol outputs. On this
basis we can then formulate extensional hyperproperties, including
\emph{noninterference modulo output ($\NIMO$)} that implies passive
simulator security. But further, we can formulate intensional
protocol properties such as probabilistic conditioning of program
distributions.

\paragraph{Fully and partially automated verification.} In Section
\ref{section-automation} we develop an automated technique, aka
certification, that verifies extensional properties of protocols such
as $\NIMO$, and also intensional properties of protocol
components. The latter include properties of protocol components that
provably guarantee security through composition in large
circuits. These compositional proofs are based on separation logic but
include novel results to support our semi-automated method for large
circuits where we (1) define certification for components, (2) certify
components, (3) prove $\NIMO$ based on the certifiedness of
components. We develop novel methods partially based on separation
logic \cite{barthe2019probabilistic} to enable (3).  In Section
\ref{section-composition} we illustrate our method to obtain
semi-automated verification methods for the GMW and Yao's Garbled
Circuit protocols, where certification can be re-used to validate new
gate implementations.

@@

Our main focus is on automated and semi-automated reasoning about
intensional properties of protocols, both through whole-program
analysis and compositional properties of program components that
support security.

Previous work on analysis for the SecreC language
\cite{almeida2018enforcing,10.1145/2637113.2637119} is concerned with
extensional properties of MPC, in particular the specification and
enforcement of declassification bounds in programs that use MPC in
subprograms. This work is explicitly reminiscent of information flow
approaches such as delimited information release
\cite{10.1007/978-3-540-37621-7_9}, downgrading policies \cite{li2005downgrading}, and
relaxed noninterference \cite{10.1145/1040305.1040319}. However, their
program logic assumes correctness of the underlying MPC protocols.
The Wys$^\star$ language \cite{wysstar}, based on Wysteria
\cite{rastogi2014wysteria}, has similar goals and includes a
trace-based semantics for reasoning about the extensional interactions
of MPC protocols. Their compiler also guarantees that underlying
multi-threaded protocols enforce the single-threaded source language
semantics which is an intensional property. \mnote{We need a clearer statement here of the flaws with Wys-star specifically} All of these systems
leverage type systems to obtain automated security analyses.

In the realm of intensional analysis, previous work has shown how to
reduce proofs of simulator security to program equivalence assertions,
which supports computer-aided verification of MPC protocols in
EasyCrypt \cite{8429300}. This work also leveraged hyperproperty
characterizations of simulator security, both passive and
active. However, their EasyCrpyt security proof constructions are
entirely manual. Probabilistic Separation Logic
\cite{barthe2019probabilistic} develops a logical framework for
reasoning about probabilistic independence in programs.  They consider
several MPC protocols and show how to systematically deduce, e.g.,
probabilistic independence of input secrets and adversarial views that
are critical intensional properties of simulator security.  However,
their focus on independence does not address the subtleties of
dependence that arise during MPC protocol execution, and the authors
do not formulate or prove simulator security properties in
\cite{barthe2019probabilistic}. The $\lambda_{\mathrm{obliv}}$
language \cite{darais2019language} is perhaps most closely related to
our work. Here, a type system is used to automatically enforce
so-called probabilistic trace obliviousness and they show how to use
their system to implement several variants of oblivious RAM. However,
obliviousness is related to noninterference and does not address
allowable information leakage as in MPC, and their use of type
linearity disallows the reuse of sampled probabilistic values which is
common in the MPC idiom, as our examples will illustrate. Similarly,
previous work on oblivious data structures \cite{10.1145/3498713},
while intended for sound integration into MPC protocols, focus on
expression and enforcement of obliviousness and do not account for
allowable information leakage.

>>>>

@@

\paragraph{Hyperproperty formulation.} In Section \ref{section-pmf} we
formulate \emph{program distributions}, a formalism for expressing
dependencies between secrets and views, useful for expressing
characteristics of protocols and precisely quantifying allowable
information leakage in terms of protocol outputs. On this basis we can
formulate security hyperproperties, including \emph{noninterference
modulo output ($\NIMO$)} that implies passive simulator security. But
program distributions are flexible and can be used to certify other
important properties of protocol components, such as probabilistic
independence, correlation, and distributions under conditioning.

\paragraph{Fully and partially automated verification.} In Section
\ref{section-automation} we develop an automated technique, aka
certification, for automatically verifying security properties such as
$\NIMO$ and other supporting properties of protocol components.  While
certification has high complexity, a compositional approach allows
certification of program components in isolation.  This enables a
semi-automated method for large circuits where we (1) define
certification for components, (2) certify components, (3) prove
$\NIMO$ based on the certifiedness of components. We develop novel
methods partially based on separation logic
\cite{barthe2019probabilistic} to enable (3).  In Section
\ref{section-composition} we illustrate our method to obtain
semi-automated verification for the GMW and Yao's Garbled
Circuit protocols, where certification can be re-used to validate new
gate implementations.

@@

Our main focus is on automated and semi-automated reasoning about
security properties of specific protocols, both through whole-program
analysis and compositional properties of program components that
support security.

Previous work on analysis for the SecreC language
\cite{almeida2018enforcing,10.1145/2637113.2637119} is concerned with
properties of complex MPC circuits, in particular a user-friendly
specification and automated enforcement of declassification bounds in
programs that use MPC in subprograms. This work is explicitly
reminiscent of information flow approaches such as delimited
information release \cite{10.1007/978-3-540-37621-7_9}, downgrading
policies \cite{li2005downgrading}, and relaxed noninterference
\cite{10.1145/1040305.1040319}. However, their program logic assumes
correctness of the underlying MPC protocols.  The Wys$^\star$ language
\cite{wysstar}, based on Wysteria \cite{rastogi2014wysteria}, has
similar goals and includes a trace-based semantics for reasoning about
the interactions of MPC protocols. Their compiler also guarantees that
underlying multi-threaded protocols enforce the single-threaded source
language semantics. However their language ultimately compiles to
protocols assumed to be secure.  All of these systems leverage type
systems to obtain automated security analyses.

In the realm of protocol verification, previous work has shown how to
reduce proofs of simulator security to program equivalence assertions,
which supports computer-aided verification of MPC protocols in
EasyCrypt \cite{8429300}. This work also leveraged hyperproperty
characterizations of simulator security, both passive and
active. However, their EasyCrpyt security proof constructions are
entirely manual. Probabilistic Separation Logic
\cite{barthe2019probabilistic} develops a logical framework for
reasoning about probabilistic independence in programs.  They consider
several MPC protocols and show how to systematically deduce, e.g.,
probabilistic independence of input secrets and adversarial views that
are critical security properties.  However, their methods are manual. 
Also, their focus on independence does not address the subtleties of
dependence that arise during MPC protocol execution, and the authors
do not formulate or prove simulator security properties in
\cite{barthe2019probabilistic}. The $\lambda_{\mathrm{obliv}}$
language \cite{darais2019language} is perhaps most closely related to
our work. Here, a type system is used to automatically enforce
so-called probabilistic trace obliviousness and they show how to use
their system to implement several variants of oblivious RAM. However,
obliviousness is related to noninterference and does not address
allowable information leakage as in MPC, and their use of type
linearity disallows the reuse of sampled probabilistic values which is
common in the MPC idiom, as our examples will illustrate. Similarly,
previous work on oblivious data structures \cite{10.1145/3498713},
while intended for sound integration into MPC protocols, focus on
expression and enforcement of obliviousness and do not account for
allowable information leakage.

### 2023-11-05 revision-1/metalang.tex
Add files via upload

    \ttt{\{ k = not flip[2,"gate:6.k"]; p =  not flip[2,"gate:6.p"]] \}}
  \end{mathpar}
}
In our implementation, gates are wired together using gate
identifiers, which are strings $w$. Top-level functionality
shown in Figure \ref{fig-ygc-lib} includes:
\begin{itemize}
\item \ttt{owl}: This function returns the output wire label for any
  gate identified by \ttt{gid}.
\item \ttt{andgate}: This defines a subprotocol for the garbler
  to define a garbled gate $\ttt{gid}$ with input wires from gates
  $\ttt{ga}$ and $\ttt{gb}$. The garbler generates keys and garbles
  the rows in YGC fashion, them with client $1$ in
  views in a standard form. For example, the view for
  a hypothetical gate 6, row 2 garbled truth table is $\ttt{v[1,gate:6tt2]}$.
  We note that garbled gates of other binary operators can be obtained with
  replacement of $\ttt{andtable}$ with appropriate garbled table definitions. 
\item \ttt{evalgate}: This defines a subprotocol for the evaluator to
  evaluate gate $\ttt{gid}$ given input wire values $\ttt{wva}$ and
  $\ttt{wvb}$.
\item \ttt{andygc}: This composes the garbler and evaluator subprotocols
  for construction and evaluation of an And gate. 
\item \ttt{garbledecode} and \ttt{evaldecode}: The former function
  defines the garbler's protocol for encrypting the circuit
  output from final gate $\ttt{gid}$, and the latter defines
  the evaluator's output decryption protocol. These are composed with \ttt{decodeygc}.
\item \ttt{encodegmw}: This defines the initial phase of the protocol,
  where the evaluator receives the wire value from their own
  secret $\sx{1}{sa}$ via $\ttt{OT}$, and the garbler communicates
  the wire value for their own secret $\sx{2}{sb}$ directly.
\end{itemize}
We provide more code details in Appendix \ref{section-ygc}, Figures
\ref{fig-ygc-aux} and \ref{fig-ygc-gates}, and complete code in our
online repository \cite{jpdf-github}.
\begin{example}
  \label{example-ygc-andcircuit}
The following program uses our YGC library to define
a circuit with a single and gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
{\small
\begin{verbatimtab}
  let secrets = encode("s1","s2") in
  v[0,output] := decode(andgg("0", secrets.wv1, secrets.wv2)) \end{verbatimtab}
}
%\begin{verbatimtab}
%  andgate(0,s1,s2);
%  garbledecode(0);
%  let secrets = encode(s1,s2) in
%  v[0,output] := decode(evalgate(0, secrets.wv1, secrets.wv2))
%\end{verbatimtab}
\end{example}

>>>>

    \ttt{\{ k = not flip[2,"gate:6.k"]; p =  not flip[2,"gate:6.p"]] \}}
  \end{mathpar}
}
In our implementation, gates are wired together using gate
identifiers, which are strings $w$. Top-level functionality
shown in Figure \ref{fig-ygc-lib} includes:
\begin{itemize}
\item \ttt{owl}: This function returns the output wire label for any
  gate identified by \ttt{gid}.
\item \ttt{andgate}: This defines a subprotocol for the garbler
  to define a garbled gate $\ttt{gid}$ with input wires from gates
  $\ttt{ga}$ and $\ttt{gb}$. The garbler generates keys and garbles
  the rows in YGC fashion, them with client $1$ in
  views in a standard form. For example, the view for
  a hypothetical gate 6, row 2 garbled truth table is $\ttt{v[1,"gate:6tt2"]}$.
  We note that garbled gates of other binary operators can be obtained with
  replacement of $\ttt{andtable}$ with appropriate garbled table definitions. 
\item \ttt{evalgate}: This defines a subprotocol for the evaluator to
  evaluate gate $\ttt{gid}$ given input wire values $\ttt{wva}$ and
  $\ttt{wvb}$.
\item \ttt{andygc}: This composes the garbler and evaluator subprotocols
  for construction and evaluation of an And gate. 
\item \ttt{garbledecode} and \ttt{evaldecode}: The former function
  defines the garbler's protocol for encrypting the circuit
  output from final gate $\ttt{gid}$, and the latter defines
  the evaluator's output decryption protocol. These are composed with \ttt{decodeygc}.
\item \ttt{encodegmw}: This defines the initial phase of the protocol,
  where the evaluator receives the wire value from their own
  secret $\sx{1}{sa}$ via $\ttt{OT}$, and the garbler communicates
  the wire value for their own secret $\sx{2}{sb}$ directly.
\end{itemize}
We provide more code details in Appendix \ref{section-ygc}, Figures
\ref{fig-ygc-aux} and \ref{fig-ygc-gates}, and complete code in our
online repository \cite{jpdf-github}.
\begin{example}
  \label{example-ygc-andcircuit}
The following program uses our YGC library to define
a circuit with a single and gate and input secrets $\ttt{s1}$ and
$\ttt{s2}$ from client's 1 and 2 respectively. 
{\small
\begin{verbatimtab}
  let secrets = encode("s1","s2") in
  v[0,"output"] := decode(andgg("0", secrets.wv1, secrets.wv2)) \end{verbatimtab}
}
%\begin{verbatimtab}
%  andgate(0,s1,s2);
%  garbledecode(0);
%  let secrets = encode(s1,s2) in
%  v[0,output] := decode(evalgate(0, secrets.wv1, secrets.wv2))
%\end{verbatimtab}
\end{example}

### 2023-11-05 revision-1/proofs.tex
Add files via upload

\begin{proof}
  Given preconditions we have $v_1 =  \{ \ttt{k = }\be^1_{k}; \ttt{p = }\be^1_{p} \}$ and
  $v_2 = \{ \ttt{k = }\be^2_{k}; \ttt{p = }\be^2_{p} \}$ for some
  $\be^1_{k}$,$\be^2_{k}$,$\be^1_{p}$,$\be^2_{p}$ with correlations as per Definition
  \ref{definition-gc}.
  %\begin{eqnarray*}
  %  v_1 &=& \{ \ttt{k = }\be^1_{k}; \ttt{p = }\be^1_{p} \} \\
  %  v_2 &=& \{ \ttt{k = }\be^2_{k}; \ttt{p = }\be^2_{p} \}
  %\end{eqnarray*}
  Let $\prog$ be as defined in Definition \ref{definition-ygcgate-certification}.
  We observe:
  \begin{eqnarray*}
    &\prog_2 = \\
    &{\small \prog[\be^1_{k}/\ttt{flip[2,"gate:a.k"]}][\be^1_{p}/\ttt{flip[2,"gate:a.p"]}][\be^2_{k}/\ttt{flip[2,"gate:b.k"]}][\be^1_{p}/\ttt{flip[2,"gate:b.p"]}]}
  \end{eqnarray*}
  Given that $g_1$ and $g_2$ are distinct and not wired in $\prog_1$
  we are assured that $\ttt{owl}(g_1)$ and $\ttt{owl}(g_1)$ are in
  independent uniform distributions, and given that $g \not\in
  \prog_1$ we are assured that $\ttt{owl}(g)$ contains entirely fresh
  flips. Thus by condition (i) of Definition \ref{definition-ygcgate-certification} and
  Lemma \ref{lemma-substitution} we have:
  $$
  \sep{\prog_1;\prog_2}{\vars(\be^1_{k},\be^2_{k},\be^1_{p},\be^2_{p})}{\vdefs(\prog_2)}
  $$
  Thus by Lemmas \ref{lemma-noninterference} and \ref{lemma-separation} we establish
  postconditions (ii) and (iii).

>>>>

\begin{proof}
  Given preconditions we have $v_1 =  \{ \ttt{k = }\be^1_{k}; \ttt{p = }\be^1_{p} \}$ and
  $v_2 = \{ \ttt{k = }\be^2_{k}; \ttt{p = }\be^2_{p} \}$ for some
  $\be^1_{k}$,$\be^2_{k}$,$\be^1_{p}$,$\be^2_{p}$ with correlations as per Definition
  \ref{definition-gc}.
  %\begin{eqnarray*}
  %  v_1 &=& \{ \ttt{k = }\be^1_{k}; \ttt{p = }\be^1_{p} \} \\
  %  v_2 &=& \{ \ttt{k = }\be^2_{k}; \ttt{p = }\be^2_{p} \}
  %\end{eqnarray*}
  Let $\prog$ be as defined in Definition \ref{definition-ygcgate-certification}.
  We observe:
  \begin{eqnarray*}
    &\prog_2 = \\
    &\begin{array}{l}\prog[\be^1_{k}/\ttt{flip[2,"gate:a.k"]}][\be^1_{p}/\ttt{flip[2,"gate:a.p"]}]\\
       \phantom{\prog}[\be^2_{k}/\ttt{flip[2,"gate:b.k"]}][\be^1_{p}/\ttt{flip[2,"gate:b.p"]}]\end{array}
  \end{eqnarray*}
  Given that $g_1$ and $g_2$ are distinct and not wired in $\prog_1$
  we are assured that $\ttt{owl}(g_1)$ and $\ttt{owl}(g_1)$ are in
  independent uniform distributions, and given that $g \not\in
  \prog_1$ we are assured that $\ttt{owl}(g)$ contains entirely fresh
  flips. Thus by condition (i) of Definition \ref{definition-ygcgate-certification} and
  Lemma \ref{lemma-substitution} we have:
  $$
  \sep{\prog_1;\prog_2}{\vars(\be^1_{k},\be^2_{k},\be^1_{p},\be^2_{p})}{\vdefs(\prog_2)}
  $$
  Thus by Lemmas \ref{lemma-noninterference} and \ref{lemma-separation} we establish
  postconditions (ii) and (iii).
